My title

### 2023-03-15 outputs/paper/paper.qmd
Added summary statistics graphs and results graphs to Quarto document

## import averaged variable datasets 
mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
mean_edu <- read.csv(here::here("outputs/data/mean_edu.csv"))
mean_happy <- read.csv(here::here("outputs/data/mean_happy.csv"))
mean_income <- read.csv(here::here("outputs/data/mean_income.csv"))
mean_marital <- read.csv(here::here("outputs/data/mean_marital.csv"))
mean_race <- read.csv(here::here("outputs/data/mean_race.csv"))
mean_sex <- read.csv(here::here("outputs/data/mean_sex.csv"))

@@

## 2.1 Overview of Data

### 2.1.1 Data Source

### 2.1.2 Variables of Interest

@@

## 2.2 Survey

## 2.3 Questionnaire

@@

@@

@@

# number of children and marital status
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = childs, fill = marital)) + 
  geom_bar(position = "dodge2")

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Average Weekly Total of Internet Use by Marital Status
#| echo: false
## Marital 
# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Average Internet Usage Hours"
  )
```

>>>>

## import averaged variable datasets 
mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
mean_edu <- read.csv(here::here("outputs/data/mean_edu.csv"))
mean_happy <- read.csv(here::here("outputs/data/mean_happy.csv"))
mean_income <- read.csv(here::here("outputs/data/mean_income.csv"))
mean_marital <- read.csv(here::here("outputs/data/mean_marital.csv"))
mean_race <- read.csv(here::here("outputs/data/mean_race.csv"))
mean_sex <- read.csv(here::here("outputs/data/mean_sex.csv"))
mean_childs <- read.csv(here::here("outputs/data/mean_childs.csv"))

@@

## 2.1 Survey

Saku

### 2.1.1 Key Features

Saku

### 2.1.2 Methodology

Saku

### 2.1.3 Strengths & Weaknesses

Saku

## 2.2 Questionnaire

Saku

## 2.3 Overview of Data

### 2.3.1 Data Source

### 2.3.2 Variables of Interest

@@

Table :)

```{r}
#| label: fig-agesidebyside
#| fig-cap: Caption
#| fig-subcap: ["Subcaption"]
#| layout-ncol: 2
#| echo: false
#| warning: false

# bar graph showing relationship between age and sex
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = age, fill = sex)) + 
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  geom_bar(position = "dodge2")

# bar graph showing relationship between age and sex
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = age, fill = race)) + 
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  geom_bar(position = "dodge2")
```

@fig-agesidebyside

```{r}
#| label: fig-childsandmarital
#| fig-cap: Caption
#| echo: false

# bar graph showing relationship between number of children and marital status
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = childs, fill = marital)) + 
  geom_bar(position = "dodge2")
```

@fig-childsandmarital

```{r}
#| label: fig-happiness
#| fig-cap: Caption
#| echo: false

# bar graph showing the different levels of happiness and number of respondents for each response
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = happy)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  labs(x = "Level of Happiness", y = "Number of Respondents")

@fig-happiness

@@

Max - might emit...

@@

Max - might emit

# use tidyverse-style code to pivot and summarise the data 
mean_childs |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Number of Children",
    y = "Internet Usage Hours"
  )
```

@@

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Average Weekly Total of Internet Use by Marital Status
#| echo: false

# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Average Internet Usage Hours"
  )
```
